Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2019-08-28 size_differentiated_export.tex
Updates from Overleaf

A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2008,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.

@@

Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}. The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}. Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.

>>>>

A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2013b,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.

@@

Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}. The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}. Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
